Response to the defense feedback

### 2021-06-14 Appendix-A/Appendix-A.tex
Updates from Overleaf

% !TEX root = ../YourName-Dissertation.tex
\Appendix{Abacus Usage Manual}

@@

Abacus analyzes vulnerabilities on the binary executable. Here we build it into  a 32-bit ELF executable. Note that while Abacus can work on stripped binaries without the source code, we use debug information to get a more detailed result (e.g., the line number in the source code) in this example.
\begin{lstlisting}[language=bash]
$ cd examples
$ gcc -m32 -g example1.c
\end{lstlisting}

@@

As expected, it shows that the function \textsf{is\_odd} has one secret-dependent control-flow vulnerability at line 5. Also, Abacus shows the vulnerability leaks 1 bit information.

>>>>

% !TEX root = ../YourName-Dissertation.tex
\Appendix[Abacus Usage Manual]{Abacus Usage Manual\footnote{The original manual was published in~\cite{9402288}.}}

@@

\tool{} analyzes vulnerabilities on the binary executable. Here we build it into  a 32-bit ELF executable. Note that while \tool{} can work on stripped binaries without the source code, we use debug information to get a more detailed result (e.g., the line number in the source code) in this example.
\begin{lstlisting}[language=bash]
$ cd examples
$ gcc -m32 -g example1.c
\end{lstlisting}

@@

As expected, it shows that the function \textsf{is\_odd} has one secret-dependent control-flow vulnerability at line 5. Also, \tool{} shows the vulnerability leaks 1 bit information.
